\subsection{CPPSLOW-INT-20-10: Periodic Calibration Products Production Service}
\label{cppslow-int-20-10}

\subsubsection{Requirements}

DMS-REQ-0059,DMS-REQ-0060,DMS-REQ-0061,DMS-REQ-0062,DMS-REQ-0063,DMS-REQ-0130,DMS-REQ-0132,DMS-REQ-0265,DMS-REQ-0282,DMS-REQ-0283,DMS-REQ-0289,DMS-REQ-0294,DMS-REQ-0314,DMS-REQ-0346.

\subsubsection{Test items}

This test will check:

\begin{itemize}

  \item{That a service exists which will execute the periodic Calibration Products Production payload;}

  \item{That all data products required are produced and persisted when that payload is executed;}

  \item{That provenance information about the production is recorded appropriately;}

  \item{That input data is retained at the end of the production.}

\end{itemize}

\subsubsection{Intercase dependencies}

\begin{note}
  Also dependent on various pieces of compute middleware and the hardware
  system, for which test cases have not yet been written.
\end{note}

\begin{itemize}
  \item{\hyperref[cppslow-int-20-00]{CPPSLOW-INT-20-00},}
  \item{\hyperref[cppslow-int-20-05]{CPPSLOW-INT-20-05}.}
\end{itemize}

\subsubsection{Input specification}

The same input is required as for
\hyperref[cppslow-int-20-05]{CPPSLOW-INT-20-05}, with the additional caveat
that the repository containing the data must be available and accessible using
the Data Backbone.

\subsubsection{Output specification}

As for \hyperref[cppslow-int-20-05]{CPPSLOW-INT-20-05}, with the additional
caveats that:

\begin{itemize}

  \item{Information must be persisted to the Data Backbone, not simply to a
  locally accessible repository;}

  \item{\textit{Input} data must be demontrated to remain available and
  unchanged on the Data Backbone at the end of the test.}

\end{itemize}

In addition, metadata describing the provenance of the data products must be
recorded and made available for inspection.

\subsubsection{Procedure}

A periodic calibration products production is scheduled and executed using the
Template \& Calibration Products Periodic Execution Service
(\citeds{LDM-148}).

The operator will monitor system logs and check for successful execution of
the service.

At the end of the service, all products specified in the output specification
above must be accessible on the Data Backbone. They should be retrieved and
checked for validity by the operator (or designated representative).
