\subsection{\textsc{cppslow-int-20-00}: Manual Calibration Products Production Execution}
\label{cppslow-int-20-00}

\subsubsection{Requirements}

DMS-REQ-0059,DMS-REQ-0060,DMS-REQ-0061,DMS-REQ-0062,DMS-REQ-0063,DMS-REQ-0130,DMS-REQ-0282,DMS-REQ-0283,DMS-REQ-0289,DMS-REQ-0308.

\subsubsection{Test items}

This test will check:

\begin{itemize}

  \item{That a single point of entry exists, in the form of a command line
  task or equivalent tool, which provides all the necessary functionality and
  configuration to perform a periodic calibration products production.}

\end{itemize}

\subsubsection{Intercase dependencies}

Generating a complete set of calibration products depends on successful
completion of:

\begin{itemize}

  \item{\hyperref[cppslow-ver-00-00]{CPPSLOW-VER-00-00}}
  \item{\hyperref[cppslow-ver-00-05]{CPPSLOW-VER-00-05}}
  \item{\hyperref[cppslow-ver-00-10]{CPPSLOW-VER-00-10}}
  \item{\hyperref[cppslow-fun-10-00]{CPPSLOW-FUN-10-00}}
  \item{\hyperref[cppslow-fun-10-05]{CPPSLOW-FUN-10-05}}
  \item{\hyperref[cppslow-fun-10-10]{CPPSLOW-FUN-10-10}}
  \item{\hyperref[cppslow-fun-10-15]{CPPSLOW-FUN-10-15}}
  \item{\hyperref[cppslow-fun-10-20]{CPPSLOW-FUN-10-20}}
  \item{\hyperref[cppslow-fun-10-25]{CPPSLOW-FUN-10-25}}
  \item{\hyperref[cppslow-fun-10-30]{CPPSLOW-FUN-10-30}}
  \item{\hyperref[cppslow-fun-10-35]{CPPSLOW-FUN-10-35}}

\end{itemize}

However, this test case may also be executed at intermediate stages during
construction to test the production of only a limited set of calibration
products, and the dependency list may be reduced as appropraite.

\subsubsection{Input specification}

A Butler data repository with all required inputs for the calibration products
production loaded. This includes:

\begin{itemize}

  \item{Dark frames corresponding to the CCDs under test;}
  \item{Flat field frames corresponding to the CCDs under test;}
  \item{Pocket pumping exposures corresponding to the CCDs under test;}
  \item{Zero-second exposures of the CCDs under test;}
  \item{Collimated Beam Projector observations per \citeds{LDM-151} \S4.2.10;}
  \item{Monochromatic flat field images corresponding to the CCDs under test.}

\end{itemize}

In addition, a pipeline configuration will be specified which includes details
of the input repository and (if necessary) any configuration overrides
required to process the data under test\footnote{The default pipeline
configuration should be appropriate for full LSST camera images, but may need
adjusting to match the test conditions or input data source.}.

\subsubsection{Output specification}

A Butler data repository should be populated with all the required period
Calibration Products Production data products, to include:

\begin{itemize}

  \item{Bad pixel lists;}
  \item{Bias images;}
  \item{Crosstalk correction matrices;}
  \item{Illumination correction frames;}
  \item{Monochromatic flat field data cubes;}
  \item{Broad-band synthetic flats;}
  \item{Dark current correction frames;}
  \item{Fringe correction frames.}

\end{itemize}

\subsubsection{Procedure}

The Calibration Products Pipeline will be invoked manually from the command
line, being provided with the configuration file needed.

At the end of processing, all of the outputs specified shall be available for
retrieval from the Butler data repository.
