\subsection{\textsc{cppslow-fun-10-00}: Bad pixel map generation}
\label{cppslow-fun-10-00}

\subsubsection{Requirements}

DMS-REQ-0059,DMS-REQ-0130.

\subsubsection{Test items}

This test will check:

\begin{itemize}

  \item{That a pipeline task (or equivalent tool) exists which generates a list
  of ``bad'' (unusable) pixels for one or more CCDs.}

\end{itemize}

\subsection{Intercase dependencies}

None.

\subsubsection{Input specification}

\begin{note}
Detailed specification of the inputs required to generate an appropriate list of
bad pixels will require further thought \& input from the Calibration Scientist;
this is a work in progress.
\end{note}

\begin{itemize}

  \item{A pre-existing list of known-bad pixels for the CCD under test. This is a Camera Team
  deliverable from sensor acceptance testing.}

  \item{Dark frames corresponding to the CCD under test. (How many? Where from —
  do they need to be on sky, or can we generated them from the test stand?)}

  \item{Flat field frames corresponding to the CCD under test. (How many? Where from —
  do they need to be on sky, or can we generated them from the test stand?)}

  \item{``Pocket pumping'' exposures corresponding to the CCD under test.  (How
  many? Where from — do they need to be on sky, or can we generated them from
  the test stand?)}

\end{itemize}

These products should be available within a Butler repository accessible
through the regular LSST data access framework from the system on which the test
is being run.

\subsubsection{Output specification}

\begin{itemize}

  \item{A list of bad pixels in the CCD under test.}

\end{itemize}

These products should be persisted to a Butler repository accessible through
the regular LSST data access framework from the system on which the test is
being run.

\subsubsection{Procedure}

The task for generating bad pixel masks will be executed from the command line,
with a configuration appropriate for it to fetch required input data from the
input Butler repository.

The resulting bad pixel list will be persisted to the output repository. To
check for correctness, it should be:

\begin{itemize}

  \item{Compared to the initial list of bad pixels provided by the Camera Team;}
  \item{Optionally overplotted on the input data for manual inspection.}

\end{itemize}
