\subsection{DRP-00-15: Scientific Verification of Source Catalog}
\label{drp-00-15}

\subsubsection{Requirements}

DMS-REQ-0334, DMS-REQ-0267, DMS-REQ-0347, DMS-REQ-0331.

\subsubsection{Test items}
\label{drp-00-15-items}

This test will check that the source catalogs delivered by the DRP science
payload meet the requirements laid down by \citeds{LSE-61}.

Specifically, this will demonstrate that:

\begin{itemize}

  \item{Measurements in the catalog are presented in flux units
  (DMS-REQ-0347);}
  \item{Derived quantities are provided in pre-computed columns
  (DMS-REQ-0331)};
  \item{..... science V\&V .....}

\end{itemize}

\subsubsection{Intercase dependencies}

\begin{itemize}

  \item{\hyperref[drp-00-00]{DRP-00-00}}
  \item{\hyperref[drp-00-10]{DRP-00-10}}

\end{itemize}

\subsubsection{Environmental needs}

\paragraph{Hardware}

The test shall be carried out on a machine with at least 16\,GB of RAM and
multiple CPU cores which has access to the \texttt{/datasets} shared (GPFS)
filesystem at the LSST Data Facility.

\paragraph{Software}

Release 14.0 of the DM Software Stack will be pre-installed (following the
procedure described in \hyperref[drp-00-00]{DRP-00-00}).

\subsubsection{Input specification}

A complete processing of the Hyper Suprime-Cam ``RC2'' dataset, as defined
at ...

\begin{note}
This dataset is currently being defined in DM-11345. We need to make sure the
results of that ticket are clearly published somewhere to complete this test
spec.

\end{note}

... through the DRP Science Payload.

This dataset shall be made available in a standard LSST data repository,
accessible via the ``Data Butler''.

It is not required that all combinations of visit and CCD have been processed
successfully: a number of failures are expected. However, documentation to
describe processing failures should be provided.

\subsubsection{Output specification}

None.

\subsubsection{Procedure}

\begin{itemize}

  \item{The DM Stack shall be initialized using the \texttt{loadLSST} script
  (as described in \hyperref[drp-00-00]{DRP-00-00}).}

  \item{A ``Data Butler'' will be initialized to access the repository.}

  \item{For each processed CCD, the source catalog will be retrieved by the
  butler and ... some stuff ... will be checked.}

\end{itemize}
